A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-08-08 paper/elsarticle/elsarticle-template.tex
paper

\usepackage{lineno,hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{amsmath}
\modulolinenumbers[5]

@@

More generally, keystone correction for planar scenes can be said to reduce to computing a 2D homography \cite{Hartley2004}, an invertible transformation that preserves colinearity and is thus fittingly alternatively referred to as a `colineation'; this is the case whether computing the homography relies on manual interaction as in the case of Pinharez, or is obtained free of manual interaction as in ours. The intuition for why it is that a transformation that preserves colinearity---i.e., maps lines to lines---can serve to model an appropriate corrective image warp can be drawn from considering a planar chessboard pattern: looking at an image of a chessboard acquired from an oblique angle, one observes that lines parallel in the chessboard appear to meet in respective vanishing points; looking at an image of the same chessboard acquired frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp the former image (where lines parallel in the scene meet in respective vanishing points) such that the lines of the chessboard appear as in the latter image (where lines parallel in the scene meet at infinity), a transformation that maps lines to lines is sufficient.

@@

\paragraph{Plane-induced homography} Let $\mathtt{K}_\text{proj}$ express the calibration matrix of the recovered projector and $(\mathtt{R}, \mathbf{t}) \in SE(3)$ the rigid body transformation that transforms points from the coordinate frame of the recovered projector to that of the virtual projector, for a given target location. Moreover, let $(\mathbf{n}^\top, -d)^\top$ give the scene plane, expressed in the coordinate frame of the recovered projector, where $\mathbf{n} \in \mathbb{R}^3$ is the scene plane's normal vector and $d = \mathbf{n}^\top\mathbf{X}$ for any point~$\mathbf{X}$ in the plane, so that $(\mathbf{n}^\top, -d) (\mathbf{X}^\top, 1)^\top = 0$. The transformation that warps the image to be projected to the scene plane by the recovered projector such that it appear as if were projected to the scene plane by the virtual projector (cf.\ Figure~\ref{fig:warp}(b)) is given the by the $3~\times~3$ matrix
\begin{equation}
\mathtt{H} = \mathtt{K}_\text{proj}\left(\mathtt{R} - \frac{\mathbf{t}\mathbf{n}^\top}{d}\right)\mathtt{K}_\text{proj}^{-1},
\label{homgen}
\end{equation}
a form of `plane-induced' 2D homography \cite{Hartley2004}. For convenience, we enable optional rotation of the image to be projected \textit{before} applying $\mathtt{H}$, about the image center; that rotation, parameterized in degrees, is thus in effect likewise carried out intuitively in accordance with the placement of the camera.

@@

The hardware setup employed in the evaluation (cf.\ Figure \ref{fig:eval}(a)) comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information,Rupprecht2021}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downwards-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m. At this height, the pixel size (i.e., length or width of a pixel if projected to the scene plane) of the camera was ca.\ 3.5 mm.

@@

\paragraph{Our approach} We began by carrying out a calibration of the camera, acquiring 10 camera calibration images (cf.\ Section~\ref{sec:approach:geometry}) of a chessboard calibration pattern with $6~\times~4$ corners ($7~\times~5$ squares) and feeding the images as input to our camera calibration module. Separately, for each of the 15 target locations, we produced a projector calibration image (cf.\ again Section~\ref{sec:approach:geometry}) by projecting a $11~\times~4$ asymmetrical circle pattern image to the location in question using the steerable mirror, placing a chessboard pattern beside the projected pattern, and acquiring the image using the downwards-facing camera. We then fed these images alongside the output of the camera calibration module to our projector calibration module. For each of the target locations, the steerable mirror was made to point to that location, the asymmetrical circle pattern image was projected to the scene plane, an image was acquired using the camera, and the location was registered in the MDC-X software as a preset. The output of the projector calibration module is a homography per input projector calibration image (cf.\ Section~\ref{sec:approach:homography}). Next, we warped the images to be projected to the respective locations using their corresponding homography, using a third dedicated custom module. These warped images were finally imported into the MDC-X software and associated with their respective location presets (cf.\ Figure \ref{fig:eval}(b)).

The total amount of time to carry out all the above steps amounted to ca.\ 20 min, with ca.\ 2 min going to acquisition of the camera calibration images, and ca.\ 5 min going to that of projector calibration images. The remainder of the time was spent running our modules or working with the MDC-X software. Note that once the camera is calibrated, that calibration can be reused if the camera's intrinsics remain fixed, in particular if no change is made to the zoom factor of the camera.

... At height above ground of 3.5 m, the pixel size was approximately 3.5 mm. Standard deviation of all measured sides was in all instances below the pixel size.

>>>>

\usepackage{lineno,hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{amsmath}
\usepackage{array}
\usepackage{booktabs}
\modulolinenumbers[5]

@@

More generally, keystone correction for planar scenes can be said to reduce to computing a 2D homography \cite{Hartley2004}, an invertible transformation that preserves colinearity and is thus fittingly alternatively referred to as a `colineation'; this is the case whether computing the homography relies on manual interaction as in the case of Pinharez, or is obtained free of manual interaction as in ours. The intuition for why it is that a transformation that preserves colinearity---i.e., maps lines to lines---can serve to model an appropriate corrective image warp can be drawn from considering a planar chessboard pattern: looking at an image of a chessboard acquired from an oblique angle, one observes that lines parallel in the chessboard appear to meet in respective vanishing points; looking at an image of the same chessboard acquired frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp the former image (where lines parallel in the scene meet in respective vanishing points) such that the lines of the chessboard appear as in the latter image (where lines parallel in the scene meet at infinity) calls for a transformation that maps lines to lines.

@@

\paragraph{Plane-induced homography} Let $\mathtt{K}_\text{proj}$ express the calibration matrix of the recovered projector and $(\mathtt{R}, \mathbf{t}) \in SE(3)$ the rigid body transformation that transforms points from the coordinate frame of the recovered projector to that of the virtual projector, for a given target location. Moreover, let $(\mathbf{n}^\top, -d)^\top$ give the scene plane, expressed in the coordinate frame of the recovered projector, where $\mathbf{n} \in \mathbb{R}^3$ is the scene plane's normal vector and $d = \mathbf{n}^\top\mathbf{X}$ for any point~$\mathbf{X}$ in the plane, so that $(\mathbf{n}^\top, -d) (\mathbf{X}^\top, 1)^\top = 0$. The transformation that warps the image to be projected to the scene plane by the recovered projector such that it appear as if were projected to the scene plane by the virtual projector (cf.\ Figure~\ref{fig:warp}(b)) is given the by the $3~\times~3$ matrix
\begin{equation}
\mathtt{H} = \mathtt{K}_\text{proj}\left(\mathtt{R} - \frac{\mathbf{t}\mathbf{n}^\top}{d}\right)\mathtt{K}_\text{proj}^{-1},
\label{homgen}
\end{equation}
a form of `plane-induced' 2D homography \cite{Hartley2004}. For convenience, we enable optional rotation of the image to be projected \textit{before} applying $\mathtt{H}$, about the image center; that rotation, parameterized in degrees, is thus in effect carried out---likewise intuitively---with respect to the ground plane.

@@

The hardware setup employed in the evaluation (cf.\ Figure \ref{fig:eval}(a)) comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information,Rupprecht2021}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downwards-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m. At this height, the pixel size (i.e., length or width of a pixel if projected to the scene plane) of the camera was 3.5 mm.

@@

\begin{table}[ht]
\caption{Deviations in measured lengths from 50~cm~$\times$~31.25~cm across the 15 augmentations produced using our approach, provided in cm and in pixel units of the downwards-facing camera (pixel size 3.5 mm). Note that in no instance do mean and standard deviation exceed 1 pixel from the viewpoint of the camera.}
\label{table:length}
\centering
{\small
\begin{tabularx}{7.4cm}{r p{1cm} p{1cm} p{1cm} p{1cm}}
\toprule
  & Top & Bottom & Left & Right \\
\midrule
Mean {\tiny[cm]} & 0.03 & 0.07 & 0.09 & 0.06 \\
Stdev {\tiny[cm]} & 0.33 & 0.17 & 0.17 & 0.17 \\
\midrule
Mean {\tiny[px]} & 0.1 & 0.19 & 0.26 & 0.18 \\
Stdev {\tiny[px]} & 0.95 & 0.48 & 0.49 & 0.49 \\
\bottomrule
\end{tabularx}}
\end{table}

\begin{table}[ht]
\caption{Deviations in measured angles from $90^\circ{}$ across the 15 augmentations produced using our approach.}
\label{table:angle}
\centering
{\small
\begin{tabularx}{6.4cm}{r p{1.75cm} p{1.75cm}}
\toprule
  & Top Right & Bottom Left\\
\midrule
Mean {\tiny[deg]} & -0.03 & 0.0 \\
Stdev {\tiny[deg]} & 0.4 & 0.34 \\
\bottomrule
\end{tabularx}}
\end{table}

\paragraph{Our approach} We began by carrying out a calibration of the camera, acquiring 10 camera calibration images (cf.\ Section~\ref{sec:approach:geometry}) of a chessboard calibration pattern with $6~\times~4$ corners ($7~\times~5$ squares) and feeding the images as input to our camera calibration module. Separately, for each of the 15 target locations, we produced a projector calibration image (cf.\ again Section~\ref{sec:approach:geometry}) by projecting a $11~\times~4$ asymmetrical circle pattern image to the location in question using the steerable mirror, placing a chessboard pattern beside the projected pattern, and acquiring the image using the downwards-facing camera. We then fed these images alongside the output of the camera calibration module to our projector calibration module. For each of the target locations, the steerable mirror was made to point to that location, the asymmetrical circle pattern image was projected to the scene plane, an image was acquired using the camera, and the location was registered in the MDC-X software as a preset. The output of the projector calibration module is a homography per input projector calibration image (cf.\ Section~\ref{sec:approach:homography}). Next, we warped the images to be projected to the respective locations using their corresponding homography, using a third dedicated custom module. These warped images were finally imported into the MDC-X software and associated with their respective location presets (cf.\ Figure~\ref{fig:eval}(b)).

Tables~\ref{table:length} and \ref{table:angle} give the deviations in measured lengths and angles, respectively, from the intended quantities. Lengths were measured using a measuring tape for the top, bottom, left, and right sides of the augmentations; angles were measured using an angle gauge at the augmentations' top-left and bottom-right corners (the measuring tape and angle gauge are both visible in Figure~\ref{fig:eval}(b)). Note that if deviations in measured lengths are expressed in units of pixels of the downwards-facing camera, mean and standard deviation in no instance exceed 1 pixel. The total amount of time expended for carrying out all the above steps amounted to ca.\ 20 min, with ca.\ 2 min going to acquisition of the camera calibration images, and ca.\ 5 min going to that of projector calibration images. The remainder of the time was spent running our modules or working with the MDC-X software. Note that once the camera is calibrated, that calibration can be reused if the camera's intrinsics remain fixed, in particular if no change is made to the zoom factor or focus settings of the camera.
